### 2014-09-23 LaTeX/RhodiumEmp.tex
updated intro and other stuff
cleaning
updates
plots in paper

To measure economic performance we use annual percent change in GDP, which we collect from the World Development Indicators at the World Bank. We choose to focus on year over change in GDP because we expect conflicts proximate to major cities to lead to reductions in growth.\footnote{Alternative measures of economic performance would have included changes in FDI inflows or changes in GDP per capita, in using either of these measures are results remain relatively the same.} Unlike much of the extant literature in constructing our dependent variable we focus on year over change instead of a ten year average. We believe this approach to be superior because it allows us to estimate the direct effect of the conflict on economic performance in that year. A ten-year average approach might hide important variation in our dependent variable that can be explained by the proximity of conflict to economic centers.

@@

@@

@@

\begin{sidewaysfigure}[ht]
	\centering
	\includegraphics[width=.9\textwidth]{CityConfMap-crop}
	\caption{This map illustrates the geographic distribution of all conflicts, according to the PRIO Conflict Site Dataset, and major cities listed in The World Almanac from 1989 to 2008. Countries for which no armed conflicts are recorded are shaded in grey.}
	\label{fig:CityConfMap}
\end{sidewaysfigure}
\FloatBarrier

@@

\section{Results}

@@

\begin{figure}[ht]
	\centering
	\resizebox{.6\textwidth}{!}{\input{mod3CoefPlot.tex}}
	\caption{Here we show the random effect regression results on GDP growth. Darker colors indicates that the coefficient estimate is significantly different from zero at a 95\% CI, while lighter the same for a 90\% CI. Grey indicates that the estimate is not significantly different from zero at either of those intervals.}
	\label{fig:coefPlot}	
\end{figure}
\FloatBarrier

@@

\begin{figure}[ht]
	\centering
	\resizebox{.8\textwidth}{!}{\input{mod3SimPlot.tex}}
	\caption{Expected values for GDP growth based on scenarios where all variables are held to their constants but Ln(Min. Conflict Dist.) varies from its minimum to maximum. The 90\% interval of each distribution is shaded in dark grey and the 95\% in a lighter color.}
	\label{fig:simsPlot}
\end{figure}
\FloatBarrier

@@

>>>>

To measure economic performance we use logged, annual percent change in GDP, which we collect from the World Development Indicators at the World Bank. We choose to focus on year over change in GDP because we expect conflicts proximate to major cities to lead to reductions in growth.\footnote{Alternative measures of economic performance would have included changes in FDI inflows or changes in GDP per capita, in using either of these measures our results remain relatively the same.} Unlike much of the extant literature in constructing our dependent variable we focus on year over change instead of a ten year average. We believe this approach to be superior because it allows us to estimate the direct effect of the conflict on economic performance in that year. A ten-year average approach might hide important variation in our dependent variable that can be explained by the proximity of conflict to economic centers.

@@

% Might want to drop this stuff about getting city data from the almanac

@@

\begin{amssidewaysfigure}
	\centering
	\includegraphics[width=1\textwidth]{CityConfMap-crop}
	\caption{This map illustrates the geographic distribution of all conflicts, according to the PRIO Conflict Site Dataset, and major cities listed in The World Almanac from 1989 to 2008. Countries for which no armed conflicts are recorded are shaded in grey.}
	\label{fig:CityConfMap}
\end{amssidewaysfigure}
\FloatBarrier

@@

@@

\section{Results}
\label{findings}

@@

\begin{figure}
	\centering
	\begin{tabular}{cc}
		\subfloat[SubFigure 1][Capital City]{
			\resizebox{.45\textwidth}{!}{\input{mCapCoefPlot}}
		\label{fig:capCoef}} &
		\subfloat[SubFigure 2][Any City]{
			\resizebox{.45\textwidth}{!}{\input{mCityCoefPlot}}
		\label{fig:cityCoef}}
	\end{tabular}
	\caption{Regression results using conflict distance from capital city on the left, and the chart on the right shows regression results using minimum conflict distance from any major city. Darker colors indicates that the coefficient estimate is significantly different from zero at a 95\% CI, while lighter the same for a 90\% CI. Grey indicates that the estimate is not significantly different from zero at either of those intervals.}
	\label{fig:coefplot}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{tabular}{cc}
		\subfloat[SubFigure 1][Capital City]{
			\resizebox{.45\textwidth}{!}{\input{mCapSimPlot}}
		\label{fig:capCoef}} &
		\subfloat[SubFigure 2][Any City]{
			\resizebox{.45\textwidth}{!}{\input{mCitySimPlot}}
		\label{fig:cityCoef}}
	\end{tabular}
	\caption{Expected values for GDP growth based on scenarios where all variables are held to their constants but Ln(Min. Conflict Dist.) varies from its minimum to maximum. The 90\% interval of each distribution is shaded in dark grey and the 95\% in a lighter color.}
	\label{fig:simsPlot}
\end{figure}

@@

\subsection{Model Performance}

RMSE: in and out of sample

\begin{figure}
	\centering
	\resizebox{.8\textwidth}{!}{\input{rmseInOut}}
	\caption{In and out of sample performance.}
	\label{fig:rmsePlot}
\end{figure}

Model heterogeneity:

\begin{figure}
	\centering
	\resizebox{.8\textwidth}{!}{\input{crossValPlot}}
	\caption{Each row here shows the coefficient estimate of distance from rerunning the model on eight random subsamples within the dataset. All the covariates used in the initial models were included as well.}
	\label{fig:crossPlot}
\end{figure}
